### 2020-02-21 manuscript/ERL_global_C_review.Rmd
added Figs 6 & 7

@@

>>>>

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 6 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEE$. Map shows data sources ($x$ and $o$ indicate young and mature stands, respectively). Lines...  .", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Figure6.png")
```

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | Age trends and biome differences in some of the major forest C stocks: (a) aboveground biomass, (b) foliage, (c) fine roots, (d) dead wood.", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Figure7.png")
```
